---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r , echo=TRUE}
data <- read.csv("activity.csv")
data$date <- as.Date(data$date, format = "%Y-%m-%d")
```
## What is mean total number of steps taken per day?
```{r, echo=TRUE}
step <- with(data, tapply(steps, date, sum))
hist(step, breaks = 10)
print(paste0("Mean : ", as.character(mean(step, na.rm = TRUE))))
print(paste0("Median : ", as.character(median(step, na.rm = TRUE))))
```
## What is the average daily activity pattern?
```{r, echo=TRUE}
intrvl <- with(data, tapply(steps, interval, mean, na.rm = TRUE))
plot(names(intrvl),intrvl, type = "l", xlab = "Interval", ylab = "Average Steps Taken")
print(paste0("The inteval with maximum number of steps is ",names(intrvl)[which.max(intrvl)]))
```

## Imputing missing values

**The missing values have been replaced by the mean of 5-min interval.**

```{r, echo=TRUE}
sum(is.na(data))
tmp = intrvl[as.character(data$interval[is.na(data)])]
step_tot <- data$steps
step_tot[is.na(step_tot)] = tmp
new_data <- data.frame(steps = step_tot, date = data$date,interval =  data$interval)
new_step <- with(new_data, tapply(steps, date, sum, na.rm = TRUE))
hist(new_step, breaks = 10)
```

Filling of missing values have lead to an increase in the frequency of steps taken every day

## Are there differences in activity patterns between weekdays and weekends?
```{r, echo=TRUE}

```
